---
title: "TMP"
author: "Angga Fathan Rofiqy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: show
    toc_depth: 3
    number_sections: false
    toc_float:
      collapsed: true
      smooth_scroll: true
    fig_caption: true
pkgdown:
  as_is: true
---

```{r message=FALSE, warning=FALSE, include=FALSE}
#                      -=( Install & Load Package Function )=-
install_load <- function (package1, ...)  {   

   # convert arguments to vector
   packages <- c(package1, ...)

   # start loop to determine if each package is installed
   for(package in packages){

       # if package is installed locally, load
       if(package %in% rownames(installed.packages()))
          do.call('library', list(package))

       # if package is not installed locally, download, then load
       else {
          install.packages(package)
          do.call("library", list(package))
       }
   } 
}

install_load("DT","dplyr","ggplot2","gridExtra")

theme1.1 <- list(
  geom_hline(yintercept = 0, size = 1, colour="#333333"),
  theme(axis.text.x = element_text(angle = 45, hjust = 1, 
                                   margin = margin(b = 10, t=-20)),
        axis.text.y = element_text(vjust = 0.5, face = "bold", 
                                   margin = margin(l = 20, r = 0)),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        text = element_text(size = 30),
        plot.subtitle = element_text(hjust = 0.5),
        panel.background = element_rect(fill = 'transparent'),
        plot.background = element_rect(fill='transparent', color=NA),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
        ) 
)
```

> <mark style="background-color: #91CCDB">**Code/Syntax :** [File.rmd](https://github.com/Zen-Rofiqy/STA1312-PSB/blob/main/Project/Tugas%20Prak%201%20Pert%201/G1401211006_Angga-Fathan-Rofiqy_Tugas-Praktikum-1.Rmd) </mark>

# Pertemuan 1

> **Penyiapan Data (R)**

## 1. **Statistik Deskriptif**

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
```

**Daftar variabel :**

-   `Pregnancies` : Number of times pregnant

-   `Glucose` : Plasma glucose concentration a 2 hours in an oral glucose tolerance test

-   `BloodPressure` : Diastolic blood pressure (mm Hg)

-   `SkinThickness` : Triceps skin fold thickness (mm)

-   `Insulin` : 2-Hour serum insulin (mu U/ml)

-   `BMI` : Body mass index (weight in kg/(height in m)\^2)

-   `DiabetesPedigreeFunction` : Diabetes pedigree function

-   `Age` : Age (years)

-   `Outcome` : Class variable (0 or 1) 268 of 768 are 1 (diabetes), the others are 0 (tidak diabetes)

```{r}
data <- read.csv('/kaggle/input/pima-indians-diabetes-database/diabetes.csv')
summary(data)
head(data, 10)
```
