---
title: "TMP"
author: "Angga Fathan Rofiqy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: show
    toc_depth: 3
    number_sections: false
    toc_float:
      collapsed: true
      smooth_scroll: true
    fig_caption: true
pkgdown:
  as_is: true
---

# Pertemuan 1

> **Penyiapan Data (R)**

## 1. **Statistik Deskriptif**

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
```

**Daftar variabel :**

-   `Pregnancies` : Number of times pregnant

-   `Glucose` : Plasma glucose concentration a 2 hours in an oral glucose tolerance test

-   `BloodPressure` : Diastolic blood pressure (mm Hg)

-   `SkinThickness` : Triceps skin fold thickness (mm)

-   `Insulin` : 2-Hour serum insulin (mu U/ml)

-   `BMI` : Body mass index (weight in kg/(height in m)\^2)

-   `DiabetesPedigreeFunction` : Diabetes pedigree function

-   `Age` : Age (years)

-   `Outcome` : Class variable (0 or 1) 268 of 768 are 1 (diabetes), the others are 0 (tidak diabetes)

```{r}
data <- read.csv('/kaggle/input/pima-indians-diabetes-database/diabetes.csv')
summary(data)
head(data, 10)
```
